Effects of bariatric surger and weight loss on resting-state functional connectivity

### 2020-12-03 manuscript/draft_rsfmri.Rmd
fix path reference

---
title: "Effects of bariatric surger and weight loss on resting-state functional connectivity"
author:
- xxx [1]
- xxx [1][2]
- xxx [1][2][3]
- xxx [1][2]
date: 1 Max-Planck-Institute for Human Cognitive and Brain Sciences, Leipzig \newline
  2 CRC 1052 "Obesity Mechanisms", Subproject A1, University of Leipzig \newline 3
  Day Clinic for Cognitive Neurology, University Clinic Leipzig
output:
  bookdown::pdf_book: 
    fig_caption: yes
    always_allow_html: true
    number_sections: yes
    toc: yes
bibliography: "bibliography.bib"
editor_options: 
  chunk_output_type: console
---
```{r "To do", include=FALSE}

@@

library(knitr) # version 1.30
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE) # fig.height=2, fig.width=4)
options(knitr.table.format = "latex") 
# put the path to this file here (working directory for Rmarkdown):
opts_knit$set(root.dir = getwd())

```
# Abstract

@@

```{r Load data, include=FALSE}
source("get_subject_ID_group_tp_forSwE.R")
final = save_txt_for_swe(group = "all", tp = "all")

@@

<!-- DESCRIPTIVE STATISTICS --> The final sample entailed morbidly obese individuals (n = `r nrow(subj_df)`, `r nrow(filter(subj_df,Sex == "f"))` female; ages `r round(mean(subj_df$Age_BL),2)` $\pm$ `r round(sd(subj_df$Age_BL),2)` SD years (range `r min(subj_df$Age_BL)`-`r max(subj_df$Age_BL)`), that either underwent surgery (n = `r cs["Sum","KG"]`, `r cs["f","IG"]` female) or were waiting list controls (n = `r cs["Sum","KG"]`, `r cs["f","KG"]` female). The study design was quasi-experimental, as patient in the waiting control list had also been recommended to undergo bariatric surgery, but were still waiting for their health insurance's approval.
```{r baseline characteristics, include=FALSE}
dfBL <- save_txt_for_swe(group = "all", tp = "BL")

>>>>

---
title: "Effects of bariatric surger and weight loss on resting-state functional connectivity"
author:
- xxx [1]
- xxx [1][2]
- xxx [1][2][3]
- xxx [1][2]
date: 1 Max-Planck-Institute for Human Cognitive and Brain Sciences, Leipzig \newline
  2 CRC 1052 "Obesity Mechanisms", Subproject A1, University of Leipzig \newline 3
  Day Clinic for Cognitive Neurology, University Clinic Leipzig
output:
  bookdown::pdf_book: 
    fig_caption: yes
    always_allow_html: true
    number_sections: yes
    toc: yes
bibliography: "bibliography.bib"
editor_options: 
  chunk_output_type: console
---

```{r "To do", include=FALSE}

@@

library(knitr) # version 1.30
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE) # fig.height=2, fig.width=4)
options(knitr.table.format = "latex") 
# put the path to this file here (working directory for Rmarkdown):
opts_knit$set(root.dir = getwd())
```
# Abstract

@@

```{r Load data, include=FALSE}
source("code/get_subject_ID_group_tp_forSwE.R")
final = txt_for_swe(group = "all", tp = "all")

@@

<!-- DESCRIPTIVE STATISTICS --> The final sample entailed morbidly obese individuals (n = `r nrow(subj_df)`, `r nrow(filter(subj_df,Sex == "f"))` female; ages `r round(mean(subj_df$Age_BL),2)` $\pm$ `r round(sd(subj_df$Age_BL),2)` SD years (range `r min(subj_df$Age_BL)`-`r max(subj_df$Age_BL)`), that either underwent surgery (n = `r cs["Sum","KG"]`, `r cs["f","IG"]` female) or were waiting list controls (n = `r cs["Sum","KG"]`, `r cs["f","KG"]` female). The study design was quasi-experimental, as patient in the waiting control list had also been recommended to undergo bariatric surgery, but were still waiting for their health insurance's approval.
```{r baseline characteristics, include=FALSE}
dfBL <- txt_for_swe(group = "all", tp = "BL")
